% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}
% Add 'print' as an option into the square bracket to remove colours from this template for printing.

\sethyphenation[variant=american]{english}{} % Add words between the {} to avoid them to be cut

\begin{document}

	\header{Sezer}{Tanriverdioglu}           % Your name
	\lastupdated

%----------------------------------------------------------------------------------------
%   SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

	\begin{aside}
%
		\section{contact}
		Kadinlardenizi Dist.
		580. st, Aksoy Apartments
		Kusadasi / Aydin
		Turkiye
		~
		Cel +90 (535) 701 1619
		~
		sezertanriverdi
		@gmail.com
%
		\section{languages}
		Turkish
		English
%
	\end{aside}

%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------

	\section{Skills}
	\vspace{-0.4cm}
	Java, Kotlin, Git, Postgres, MongoDB, SpringBoot, JavaEE, JUnit, Docker, Redis, ApacheMQ, Kafka, Maven

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

	\section{Experience}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{2021 May--Now}
		{Just Appraised}
		{San Fransisco, California (Remote)}
		{\jobtitle{Senior Software Developer}\\
		As a Software developer at Just Appraised, I have experience working with various technologies, including ActiveMQ, PostgreSQL, AWS S3, Redis, and Unit Tests. At Just Appraised, I have used these tools to create robust, scalable, and high-performing applications for our clients.

		I have a strong understanding of the fundamentals of JavaEE, and I am always looking for ways to improve my skills and stay up to date with the latest developments in the field. I am confident in leveraging these technologies to deliver successful projects for our clients.}
%------------------------------------------------
		\entry
		{2020 Nov--2021 Apr}
		{Innovance}
		{Istanbul, Turkiye (Remote)}
		{\jobtitle{Senior Software Developer}\\
		As a Java developer at Innovance, I joined a newly-created team working on an important call center project for our client, Fibabanka. The project was developed using SpringBoot, and I was able to quickly learn the logic of the project and make valuable contributions during my time on the team.
		}
%------------------------------------------------
		\entry
		{2020 Feb--2020 Oct}
		{Etiya}
		{Istanbul, Turkiye}
		{\jobtitle{Senior Software Developer}\\
		In my new role, I had the opportunity to work closely with the architecture teams, including solution architects and software architects, and was involved in the process of designing the project.

		I also assisted in leading the newly-created backend team, which consisted mostly of junior developers. I helped the team understand the technical requirements and managed their progress to ensure that we met our goals within the given time period. I am satisfied with my ability to contribute to the development and growth of the team and am confident in my ability to lead and mentor others.
		}
%------------------------------------------------
		\entry
		{2018 Dec--2020 Feb}
		{Etiya}
		{Istanbul, Turkiye}
		{\jobtitle{Software Developer}\\
		I joined Etiya as a Backend Developer and was immediately tasked with working on an important project for a Canadian telecommunications company. The technology stack for the project included SpringBoot, PostgreSQL, ElasticSearch, ActiveMQ, and Kafka.

		During my time on the project, I made significant contributions, including the development of valuable features and solutions.

		In addition to my technical responsibilities, I also gained experience working with teams across cities and countries. This required me to effectively communicate and collaborate remotely, and I am proficient in remote working as a result.
		}
%------------------------------------------------
		\entry
		{2014 Jan--2018 Dec}
		{Idea Technology Solutions}
		{Istanbul, Turkiye}
		{\jobtitle{Software Developer}\\
		At the beginning of my career, I was a member of the mobile application development team. Our applications are consumed by many large-sized companies in Turkey and also other countries such as South Africa and Iran.
		After a few years of mobile development, I was also responsible for backend services consumed by mobile applications. Our mobile applications were designed to work offline and we re-designed these services to work offline and online together
		On the Android side, I experienced JAVA which we converted some parts to Kotlin later. On the other hand on the backend side, I developed our web services with dotnet (C\#) as Web API. I also had familiar with Oracle DB, PostgreSQL, and MySQL

		}

	\end{entrylist}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

	\section{Education}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{2009--2013}
		{Bachelor Degree {\normalfont Computer Engineering}}
		{Trakya University  |  Edirne, Turkiye}
		{\vspace{-0.3cm}}
%------------------------------------------------
	\end{entrylist}

%----------------------------------------------------------------------------------------
%   SOFT SKILLS SECTION
%----------------------------------------------------------------------------------------

	\section{Publications}
	\begin{entrylist}
%------------------------------------------------
		\entry
		{}
		{Java Book - Yeni Başlayanlar için JAVA (Turkish Name)}
		{Kodlab}
		{
			\\
			\\
			I have written a book about JAVA with a friend from university. Our main goal was to explain JAVA basics with examples to people who want to learn about JAVA.
			\\
			\\
			Yeni Başlayanlar için JAVA (Turkish Name)
			\\
			Our book has been published by Kodlab and it has been published in its 25th edition so far.

		}
		{\vspace{-0.3cm}}
	\end{entrylist}
%----------------------------------------------------------------------------------------
%   Voluntariness SECTION
%----------------------------------------------------------------------------------------

	\section{Communities}
	\begin{entrylist}
%------------------------------------------------
		\entry
		{}
		{Contributor / Mentor}
		{Turkiye Java Community}
		{
			Non-profit software community to share knowledge
			\\
			\\
			I'm helping the community to organize events and share knowledge with the community members
		}
		{\vspace{-0.3cm}}
	\end{entrylist}
%----------------------------------------------------------------------------------------
%       INTERESTS SECTION
%----------------------------------------------------------------------------------------

	\section{Interests}

	\begin{entrylist}
%------------------------------------------------
		\entry
		{Professional}
		{- {\normalfont Continue learning, work and develop a career in what I'm passionate about, which are all the information technologies. }}
		{}
		{\vspace{-0.3cm}}
%------------------------------------------------
		\entry
		{Personal}
		{- {\normalfont Be economically independent, have a balance between my work and my personal life, manage my time in the activities that I like, such as video games, music, gardening and movies }}
		{}
		{}
%------------------------------------------------
	\end{entrylist}

\end{document}