%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Senior Software Devloper} % Job title
    {Just Appraised} % Organization
    {San Fransisco, California (Remote)} % Location
    {May. 2021 - Now} % Date(s)
    {
        As a Software developer at Just Appraised, I have experience working with various technologies, including ActiveMQ, PostgreSQL, AWS S3, Redis, and Unit Tests. At Just Appraised, I have used these tools to create robust, scalable, and high-performing applications for our clients.
    I have a strong understanding of the fundamentals of JavaEE, and I am always looking for ways to improve my skills and stay up to date with the latest developments in the field. I am confident in leveraging these technologies to deliver successful projects for our clients.
    }

%---------------------------------------------------------
    \cventry
    {Senior Software Developer} % Job title
    {Innovance} % Organization
    {Istanbul, Turkiye (Remote)} % Location
    {Nov. 2020 - Apr. 2021} % Date(s)
    {
        As a Java developer at Innovance, I joined a newly-created team working on an important call center project for our client, Fibabanka. The project was developed using SpringBoot, and I was able to quickly learn the logic of the project and make valuable contributions during my time on the team.
    }

%---------------------------------------------------------
    \cventry
    {Senior Software Developer} % Job title
    {Etiya} % Organization
    {Istanbul, Turkiye} % Location
    {Feb. 2020 - Oct. 2020} % Date(s)
    {
        In my new role, I had the opportunity to work closely with the architecture teams, including solution architects and software architects, and was involved in the process of designing the project.
    I also assisted in leading the newly-created backend team, which consisted mostly of junior developers. I helped the team understand the technical requirements and managed their progress to ensure that we met our goals within the given time period. I am satisfied with my ability to contribute to the development and growth of the team and am confident in my ability to lead and mentor others.
    }

%---------------------------------------------------------
    \cventry
    {Sofware Developer} % Job title
    {Etiya} % Organization
    {Istanbul, Turkiye} % Location
    {Dec. 2018 - Feb. 2020} % Date(s)
    {
        I joined Etiya as a Backend Developer and was immediately tasked with working on an important project for a Canadian telecommunications company. The technology stack for the project included SpringBoot, PostgreSQL, ElasticSearch, ActiveMQ, and Kafka.
    During my time on the project, I made significant contributions, including the development of valuable features and solutions.
    In addition to my technical responsibilities, I also gained experience working with teams across cities and countries. This required me to effectively communicate and collaborate remotely, and I am proficient in remote working as a result.
    }

%---------------------------------------------------------
    \cventry
    {Software Developer} % Job title
    {Idea Technology Solutions} % Organization
    {Istanbul, Turkiye} % Location
    {Jan. 2014 - Dec. 2018} % Date(s)
    {
        At the beginning of my career, I was a member of the mobile application development team. Our applications are consumed by many large-sized companies in Turkey and also other countries such as South Africa and Iran.
    After a few years of mobile development, I was also responsible for backend services consumed by mobile applications. Our mobile applications were designed to work offline and we re-designed these services to work offline and online together
    On the Android side, I experienced JAVA which we converted some parts to Kotlin later. On the other hand on the backend side, I developed our web services with dotnet (C\#) as Web API. I also had familiar with Oracle DB, PostgreSQL, and MySQL
    }

%---------------------------------------------------------
\end{cventries}
\newpage