
\newpage
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Reference Links}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \begin{description}
    \item[Blog] \hfill \\
      \href{https://emre.xyz}{emre.xyz} \hfill \\
      I write about programming, technology, and my personal experiences. I also write about the things that I learn and share my knowledge with others.
    \item[GitHub] \hfill \\
      \href{https://github.com/delirehberi}{github.com/delirehberi} \hfill \\
      I have been using GitHub for a long time. I have contributed to many open source projects and also created my own projects. I am also interested in learning new technologies and programming languages.
    \item[LinkedIn] \hfill \\
    \href{https://www.linkedin.com/in/delirehberi/}{linkedin.com/in/delirehberi} \hfill \\
    I use LinkedIn to connect with other professionals and share my knowledge with others. I also use it to find new job opportunities and connect with recruiters.
    \item[Medium] \hfill \\
    \href{https://medium.com/@delirehberi}{medium.com/@delirehberi} \hfill \\
    I write about programming, technology, and my personal experiences. I also write about the things that I learn and share my knowledge with others.
    \item[Reddit] \hfill \\
    \href{https://www.reddit.com/user/aybarscengaver}{reddit.com/user/aybarscengaver} \hfill \\
    I use Reddit to connect with other professionals and share my knowledge with others.
    \item[Bluesky] \hfill \\
    \href{https://bsky.app/profile/delirehberi.emre.xyz}{bsky.app/profile/delirehberi.emre.xyz} \hfill \\
    I use Bluesky to connect with other professionals and share my knowledge with others. 
    \item[Youtube] \hfill \\
    \href{https://www.youtube.com/@delirehberi}{youtube.com/@delirehberi} \hfill \\
    I use Youtube to share my knowledge with others. 

  \end{description}
\end{cventries}
